---
title: data analysis
output: pdf_document
---
```{r setup,include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)
```
```{r}
library(tidyverse)
library(ggplot2)
```
### 2.Data cleaning
#### 2.1 Data cleaning

```{r}
survey <- read_csv("Survey.csv")
#Convert Fatty to Ordered Factor
survey <- survey %>%
  mutate(
    Fatigue = factor(
    Fatigue, 
    levels = c("Extremely fatigued", "Very fatigued", 
    "Moderately fatigued", "Slightly Fatigued", 
    "Not fatigued at all"),
    ordered = TRUE)
    )
head(survey)
```
```{r}
#Merge fatigue levels into three categories (new variable: Fatigue. 3)
survey <- survey %>%
  mutate(Fatigue.3 = case_when(
    Fatigue %in% c("Extremely fatigued", "Very fatigued") ~ "HFatigue",
    Fatigue == "Moderately fatigued" ~ "MFatigue",
    Fatigue %in% c("Slightly Fatigued", "Not fatigued at all") ~ "LFatigue"
  ),
  Fatigue.3 = factor(
    Fatigue.3, 
    levels = c("HFatigue", "MFatigue", "LFatigue")
    )
  )
head(survey)
```
```{r}
#Simplify the dominant hand to the right-handed Ye/No (new variable: RH)
survey <- survey %>%
  mutate(RH = case_when(
    PrimarilyHand == "Right hand" ~ "Y",
    TRUE ~ "N"
  ),
  RH = factor(RH, levels = c("Y", "N")))
```

```{r}
#Delete variables with very little information
survey <- survey %>% select(-AlcoholIntake)
#Convert other categorical variables into factors
survey <- survey %>%
  mutate(
    Gamer = factor(Gamer),
    CaffeinIntake = factor(CaffeinIntake),
    Stress = factor(Stress, 
                    ordered = TRUE,
                    levels = c("Very Low", 
                               "Low", 
                               "Moderate", 
                               "High", 
                               "Very High")
                    ),
    NoiseLevel = factor(NoiseLevel),
    Temperature = factor(Temperature)
  )
```
```{r}
survey
```
### 2.2 descriptive statistics

```{r}
summary(survey)
```
### 3.Exploratory data analysis

#### 3.1 Fatigue level vs reaction time (first round)

```{r,fig.width=6, fig.height=4, fig.align='center'}
ggplot(survey, aes(x = Fatigue.3, y = First, fill = Fatigue.3)) +
  geom_boxplot() +
  labs(title = "Test Scores by Fatigue Level (First Test)", x = "Fatigue Level", y = "First Test Score") +
  scale_fill_manual(values = c("HFatigue" = "red", "MFatigue" = "yellow", "LFatigue" = "green"))
```
#### 3.2 Distribution of operating system types
```{r,fig.width=6, fig.height=4, fig.align='center'}
ggplot(survey, aes(x = DeviceOS)) +
  geom_bar(fill = "lightgreen") +
  labs(title = "Distribution of Device OS", x = "Device OS", y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
#### 3.3 Comparison of weekly exercise duration and first round reaction time

```{r,fig.width=6, fig.height=4, fig.align='center'}
ggplot(survey, aes(x = AvgHoursExercise, y = First)) +
  geom_point(color = "purple") +
  labs(title = "Avg Hours of Exercise vs Reaction Time (First Try)", x = "Avg Hours of Exercise", y = "Reaction Time (ms)") +
  theme_minimal()
```

### 4 model building
#### 4.1 Multiple linear regression


```{r}
model41 <- lm(First ~ Fatigue.3 + Stress + AvgSleepTime + LastNightSleep + 
              HoursAweak + VideoGamePlay + SportsPlay + AvgHoursExercise + 
              CaffeinIntake + RH + InputDevice + DeviceOS + RefreshRate + 
              WiFi, data = survey)
summary(model41)
```
#### 4.2 ANOVA (Effects of Different Caffeine Intake and Game Duration on Sleep Duration)

```{r}
anova_model <- aov(AvgSleepTime ~ CaffeinIntake * VideoGamePlay, data = survey)
summary(anova_model)
```
```{r}
tukey_results <- TukeyHSD(anova_model)
tukey_results
```
```{r,fig.width=6, fig.height=4, fig.align='center'}
ggplot(survey, aes(x = VideoGamePlay, y = AvgSleepTime, color = CaffeinIntake)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.2)) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Effect of Caffeine Intake and Video Game Play on Average Sleep Time",
       x = "Video Game Play", y = "Average Sleep Time") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
#### 4.3 Residual Diagnosis Diagram

```{r,fig.width=6, fig.height=4, fig.align='center'}
# QQ
qqnorm(residuals(anova_model))
qqline(residuals(anova_model), col = "red")
```














